---
title: "Experis - PKPD Development"
author: "Kevin Putschko"
date: "1/14/2020"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(DT)
```

## Load the Function

Load the function with the `source()` command, where the string is the path of the `function.R` script.  
```{r source}
source("r/function.R")
```


## Test the Function

Then we run a test with the function.  In your case, it might be better to include a full filepath instead of just the folder name.  Remember that in R, filepaths must either have a single forward slash `/` or have two backslashes `\\`, because a single backslash `\` won't work.

```{r test-1}
test_output <-
  fx_file_mapping(file_map = "mapping/mapping1.csv",
                  join_keys = c("STUDYID", "USUBJID", "DOMAIN"),
                  data_folder = "data_input")
```

## Access the Output

And we access the output like this. Ignore the ` %>% head()`, because this is only for display purposes.

```{r}
test_output$output_data %>% head()
test_output$output_check %>% head()
test_output$output_message
```

